---
title: "R Notebook"
output: html_notebook
---

```{r message=FALSE, warning=FALSE}
library(clusterSim)
library(tidyverse)
library(dplyr)
library(caret)
library(ggplot2)
library(Boruta)

```


```{r}
df<-readRDS("final_data_airbnb_covid.rds")

```


### 1 Normalization: Standard Scaling

```{r}
# Standartization
data <-df
numeric_vars <- names(which(sapply(data, is.numeric)))

for (i in numeric_vars){
  data[i]<-data.Normalization (data[[i]], type="n5",normalization="column")
}

head(data)
```


## 2 Feature Selection & Finding Optimal Formula

### 2.1 Feature Selection against Target=Successful

```{r}
# Train Boruta to select features against hosts success(target variable) while excluding revenue

train_success<-data%>%dplyr::select(-revenue)

# shuffle
set.seed(42)
rows <- sample(nrow(train_success)) 
train_success <- train_success[rows, ]

# Train Boruta
train_success<-train_success[1:7000,]
boruta_success <- Boruta(suceessful~., data = train_success, maxRuns = 50, doTrace = 2)
print(boruta_success)
```


```{r}
plot(boruta_success, xlab = "", xaxt = "n")
lz<-lapply(1:ncol(boruta_success$ImpHistory),function(i)
boruta_success$ImpHistory[is.finite(boruta_success$ImpHistory[,i]),i])
names(lz) <- colnames(boruta_success$ImpHistory)
Labels <- sort(sapply(lz,median))
axis(side = 1,las=2,labels = names(Labels),
     at = 1:ncol(boruta_success$ImpHistory), cex.axis = 0.7)

```


```{r}
# Optimal formula
suc_formula<-getConfirmedFormula(boruta_success)
print(suc_formula)
#Attribute statistics
attStats(boruta_success)
```


```{r}
suceessful ~ host_response_time + host_response_rate + host_acceptance_rate + 
    host_is_superhost + neighbourhood + zipcode + is_location_exact + 
    property_type + room_type + accommodates + bathrooms + bedrooms + 
    beds + security_deposit + cleaning_fee + guests_included + 
    extra_people + minimum_nights + maximum_nights + minimum_minimum_nights + 
    maximum_minimum_nights + minimum_maximum_nights + maximum_maximum_nights + 
    minimum_nights_avg_ntm + maximum_nights_avg_ntm + availability_365 + 
    number_of_reviews + number_of_reviews_ltm + review_scores_rating + 
    review_scores_accuracy + review_scores_cleanliness + review_scores_checkin + 
    review_scores_communication + review_scores_location + review_scores_value + 
    instant_bookable + cancellation_policy + calculated_host_listings_count + 
    calculated_host_listings_count_entire_homes + calculated_host_listings_count_private_rooms + 
    reviews_per_month + zip_avg_rev + covid_cases_zip + covid_cases_city + 
    covid_cases_state + covid_cases_usa + t24_hourcheck_in + 
    Airconditioning + Bathtub + BBQgrill + Bedlinens + Buildingstaff + 
    CableTV + Carbonmonoxidealarm + Coffeemaker + Cookingbasics + 
    Dishesandsilverware + Dishwasher + Dryer + Elevator + Ethernetconnection + 
    Extrapillowsandblankets + Family_kidfriendly + Fireextinguisher + 
    Firstaidkit + Freeparkingonpremises + Freestreetparking + 
    Gardenorbackyard + Gym + Hottub + Hotwater + Internet + Keypad + 
    Kitchen + Laptop_friendlyworkspace + Laptopfriendlyworkspace + 
    Lockonbedroomdoor + Longtermstaysallowed + Luggagedropoffallowed + 
    Microwave + Nostairsorstepstoenter + Oven + PacknPlay_travelcrib + 
    Paidparkingoffpremises + Patioorbalcony + Pool + Privateentrance + 
    Refrigerator + Selfcheck_in + Ski_in_Ski_out + 
    Stairgates + Stove + Suitableforevents + TV + Washer
```


### 2.3 Feature Selection Target=Revenue
```{r message=FALSE, warning=FALSE}
train_revenue<-data%>%dplyr::select(-suceessful)
train_revenue<-train_revenue[12000:28000,]
boruta_revenue <- Boruta(revenue~., data = train_revenue, maxRuns = 50, doTrace = 2)
print(boruta_revenue)
```

```{r}
plot(boruta_revenue, xlab = "", xaxt = "n")
lz<-lapply(1:ncol(boruta_revenue$ImpHistory),function(i)
boruta_revenue$ImpHistory[is.finite(boruta_revenue$ImpHistory[,i]),i])
names(lz) <- colnames(boruta_revenue$ImpHistory)
Labels <- sort(sapply(lz,median))
axis(side = 1,las=2,labels = names(Labels),
     at = 1:ncol(boruta_revenue$ImpHistory), cex.axis = 0.7)
```

```{r}
# Get Optimal Revenue formula
rev_formula<-getConfirmedFormula(boruta_revenue)
print(rev_formula)
#Attribute statistics
attStats(boruta_revenue)
```

```{r}
revenue ~ host_response_time + host_response_rate + host_acceptance_rate + 
    host_is_superhost + neighbourhood + zipcode + is_location_exact + 
    property_type + room_type + accommodates + bathrooms + bedrooms + 
    beds + security_deposit + cleaning_fee + guests_included + 
    extra_people + minimum_nights + maximum_nights + minimum_minimum_nights + 
    maximum_minimum_nights + minimum_maximum_nights + maximum_maximum_nights + 
    minimum_nights_avg_ntm + maximum_nights_avg_ntm + availability_365 + 
    number_of_reviews + number_of_reviews_ltm + review_scores_rating + 
    review_scores_accuracy + review_scores_cleanliness + review_scores_location + 
    review_scores_value + instant_bookable + cancellation_policy + 
    calculated_host_listings_count + calculated_host_listings_count_entire_homes + 
    calculated_host_listings_count_private_rooms + reviews_per_month + 
    zip_avg_rev + covid_cases_usa + t24_hourcheck_in + 
    Bathroomessentials + Bathtub + BBQgrill + Bedlinens + Bedroomcomforts + 
    Bodysoap + Buildingstaff + CableTV + Carbonmonoxidealarm + 
    Carbonmonoxidedetector + Coffeemaker + Cookingbasics + Dishesandsilverware + 
    Dishwasher + Dryer + Elevator + Extrapillowsandblankets + 
    Family_kidfriendly + Fireextinguisher + Firstaidkit + 
    Freeparkingonpremises + Freestreetparking + Gardenorbackyard + 
    Gym + Hairdryer + Highchair + Hottub + Hotwater + Internet + 
    Keypad + Kitchen + `Laptop_friendlyworkspace` + Laptopfriendlyworkspace + 
    Lockonbedroomdoor + Lockbox + Longtermstaysallowed + Luggagedropoffallowed + 
    Microwave + Nostairsorstepstoenter + Other + Oven + `PacknPlay_travelcrib` + 
    Paidparkingoffpremises + Paidparkingonpremises + Patioorbalcony + 
    Petsallowed + Petsliveonthisproperty + Pool + Privateentrance + 
    Privatelivingroom + Refrigerator + `Selfcheck_in` + 
    Singlelevelhome + Smokealarm + Stove + Suitableforevents + 
    Toiletpaper + `translationmissing:en.hosting_amenity_50` + 
    TV + Washer
```

## 3 Training Models

### 3.1 Train & Test Split for classification
```{r message=FALSE, warning=FALSE}
#Shuffle
set.seed(42)
rows <- sample(nrow(data)) 
data_shuf <- data[rows, ]

trainIndex <- createDataPartition(data_shuf$suceessful, p=0.7, list= FALSE , times=1)

df.train<- data_shuf[trainIndex,][1:7000,] # remove the limit if you want to train on the full dataset
df.test <- data_shuf[-trainIndex,]
```



### 3.2 Survival Analysis - Train  Random Forest Classifier
```{r}
#Formula can be replaced with the variable above suc_formula

rf_cla <- train(suc_formula,
                  data=df.train,
                  method='rf',
                  metric='Accuracy',
                  ntree=20,
                  importance = TRUE)

print(rf_cla)

```


### 3.3 Train & Test Split for regression
```{r}
trainIndex <- createDataPartition(data$revenue, p=0.7, list= FALSE , times=1)


df.train<- data[trainIndex,][1:7000,] # remove the limit if you want to train  full dataset
df.test <- data[-trainIndex,]
```


### 3.4 Regression - Train the Random Forest Model
```{r}
#Formula can be replaced with the variable above rev_formula
rf_reg <- train(rev_formula,
                  data=df.train,
                  method='rf',
                  metric='RMSE',
                  ntree=20,
                  importance = TRUE)
print(rf_reg)
```

## 4 Validation

### 4.1 CLassification metrics
```{r}
prediction <- predict(rf_cla,df.test)

confusionMatrix(prediction,df.test$suceessful)
```

```{r}

table <- data.frame(confusionMatrix(prediction,df.test$suceessful)$table)

plotTable <- table %>%
  mutate(goodbad = ifelse(table$Prediction == table$Reference, "good", "bad")) %>%
  group_by(Reference) %>%
  mutate(prop = Freq/sum(Freq))

# fill alpha relative to sensitivity/specificity by proportional outcomes within reference groups (see dplyr code above as well as original confusion matrix for comparison)
ggplot(data = plotTable, mapping = aes(x = Reference, y = Prediction, fill = goodbad, alpha = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1) +
  scale_fill_manual(values = c(good = "green", bad = "red")) +
  theme_bw() +
  xlim(rev(levels(table$Reference)))
```

```{r}
pred1 <- prediction(as.numeric(prediction),df.test$suceessful)
perf1 <- performance(pred1,"tpr","fpr")

rocplot <- function(pred, truth, ...) {
  predob = prediction(pred, truth)
  perf = performance(predob, "tpr", "fpr")
  plot(perf, ...)
  area <- auc(truth, pred)
  area <- format(round(area, 4), nsmall = 4)
  text(x=0.8, y=0.1, labels = paste("AUC =", area))

  # the reference x=y line
  segments(x0=0, y0=0, x1=1, y1=1, col="gray", lty=2)
}

rocplot(as.numeric(prediction), df.test$suceessful, col="blue")
```



### 4.2 Regression metrics
```{r}

predictions <- rf_reg %>% predict(df.test)
predictions_train<- rf_reg %>% predict(df.train)

data.frame(
  R2 = R2(predictions_train, df.train$revenue),
  
  RMSE = RMSE(predictions, df.test$revenue),
  MAE = MAE(predictions, df.test$revenue)
)

```


## 4.3 Feature Importances

```{r}
#Feature Importance for the classifier

varImp(rf_cla, scale = FALSE)

```


```{r}
varImp(rf_reg, scale = FALSE)
```
